---
title: "rbtl - Research Beyond the Lab"
subtitle: "Research Data Management"  
author: "Lars Schöbitz"
date: '
  `r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: ["default", "../xaringan-themer.css", "../slides.css"]
    lib_dir: libs
    nature:
      beforeInit: "https://platform.twitter.com/widgets.js"
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
      highlightStyle: solarized-light
      highlightSpans: true
      highlightLanguage: ["r", "css", "yaml"]
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r child = "../setup.Rmd"}
```

```{r}
library(tidyverse)
library(lubridate)
```

# Today

1. Homework Assignment 5 - Review
2. Week 6 - Learning Objectives
3. Break-out groups: Pre-test & logistics
4. Planning for Week 7: Data collection
5. What's next?

---
class: inverse, middle

.big[Homework Assignment 5 - Review]

---
# Think, Pair, Share

.question[
1. Why should you never leave a blank cell in a spreadsheet used for data collection?
2. What is the benefit of having a data in a rectangular format?
]

.your-turn[
- **Think** for 2 minutes
- **Pair** with your neighbour for 4 minutes
- **Share** your answer with the class
]

```{r, echo = FALSE}

countdown(
  minutes = 2, seconds = 0,
  left = 0, right = 0,
  padding = "10px", margin = "5%",
  font_size = "2em"
)

```


---
class: inverse, middle

.big[Week 6 - Learning Objectives]

---
# Week 5 - Learning Objectives


1. Learners are able to use and trouble-shoot the survey tools of others
2. Learners are able to self-organize and prepare time and logistic plans

3. Learners understand the importance of documentation and metadata for (research) data management

---
class: inverse, middle

.big[Break-out groups: Pre-test & logistics]

