---
title: "rbtl - Research Beyond the Lab"
subtitle: "R Markdown"  
author: "Lars Schöbitz"
date: '
  `r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: ["default", "../xaringan-themer.css", "../slides.css"]
    lib_dir: libs
    nature:
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
      highlightStyle: solarized-light
      highlightSpans: true
      highlightLanguage: ["r", "css", "yaml"]
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r child = "../setup.Rmd"}
```

```{r}
library(tidyverse)
library(lubridate)
```




# Today

1. Homework Assignment 3
1. File formats
1. R Markdown 
1. Homework Assignment 4

---
class: inverse, middle

.big[Homework Assignment 3]

---
# Homework Assignment 3


---
class: inverse, middle

.big[File formats]


---
class: inverse, middle

.big[R Markdown]


---
class: inverse, middle

.big[Homework Assignment 4]



---
class: center, middle

# Thanks! `r emo::ji("sunflower")` 

Slides created via the R packages:

[**xaringan**](https://github.com/yihui/xaringan)<br>
[gadenbuie/xaringanthemer](https://github.com/gadenbuie/xaringanthemer)

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

Access slides as [PDF on GitHub](https://rbtl-fs22.github.io/website/slides/pt2-d03-reference-management/pt2-d03-reference-management.pdf)

All material is licensed under [Creative Commons Attribution Share Alike 4.0 International](https://creativecommons.org/licenses/by-sa/4.0/). 

