---
title: "rbtl - Research Beyond the Lab"
subtitle: "Tools for the course"  
author: "Lars Schöbitz"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: ["default", "../xaringan-themer.css", "../slides.css"]
    lib_dir: libs
    nature:
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
      highlightStyle: solarized-light
      highlightLanguage: ["r", "css", "yaml"]
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r child = "../setup.Rmd"}
```

```{r}
library(tidyverse)
library(palmerpenguins)
library(xaringanExtra)
```

---
# Outline

- Goals
- Assignment due dates
- GitHub
- RStudio Cloud
- RStudio IDE
- R
- Version control system

---
# Goals for today

You...

---
# Assignments 1, 2, and 3

Full points for assignment 1, 2, and 3 if submitted by 15th March

---
class: center, middle

# Thanks! `r emo::ji("sunflower")` 

Slides created via the R packages:

[**xaringan**](https://github.com/yihui/xaringan)<br>
[gadenbuie/xaringanthemer](https://github.com/gadenbuie/xaringanthemer)

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

All material is licensed under [Creative Commons Attribution Share Alike 4.0 International](https://creativecommons.org/licenses/by-sa/4.0/). 

