---
title: "rbtl - Research Beyond the Lab"
subtitle: "Data Science Lifecycle"  
author: "Lars Schöbitz"
institute: "Global Health Engineering - ETH Zurich"
date: '
  `r Sys.Date()`'
format: 
  revealjs: 
    theme: [default, "../slides.scss"]
    chalkboard: true
editor: source
---

```{r}
#| child: "../setup.Rmd"
```

```{r}
library(tidyverse)
library(lubridate)
```

```{r data}

dat_link <- "https://raw.githubusercontent.com/Global-Health-Engineering/manuscript-hospital-air-quality/main/data/intermediate/malawi-hospitals-air-quality.csv"

# The following codee uses a function calles 'read_csv()' to read the data from 
# the link that is stored in the Object dat_link. The data is then stored in a 
# new object named 'dat_in'. After running the code, the name shows up in the   
# Environment pane in the top right of window 

dat_in <- read_csv(dat_link)

dat_in_sum_day <- dat_in %>% 
  filter(value <= 1000) %>% 
  mutate(date = lubridate::as_date(date_time)) %>% 
  group_by(date, location, indicator) %>% 
  summarise(min = min(value),
            median = median(value),
            mean = mean(value),
            sd = sd(value),
            max = max(value)) %>% 
  ungroup()

```

# Data Science Lifecycle {background-color="#0F4C81"}

# dplyr {background-color="#0F4C81"}

## Rules of dplyr functions

::: {.incremental}

- First argument is always a data frame^[A footnote]
- Subsequent arguments say what to do with that data frame
- Always return a data frame  
- Don't modify in place 
 
:::

::: {.notes}
Here are my speaker notes
:::

# Code {background-color="#0F4C81"}

## Example 2

:::: {.columns}

::: {.column width="60%"}


```{r}
#| code-line-numbers: "|1|2"
dat_in_sum_day <- dat_in %>% 
  filter(value <= 1000) %>% 
  mutate(date = as_date(date_time)) %>% 
  group_by(date, location, indicator) %>% 
  summarise(min = min(value),
            median = median(value),
            mean = mean(value),
            sd = sd(value),
            max = max(value)) 
```

:::

::: {.column width="40%"}

- What is `%>%`?
- What is the `<-` sign?
- What are `dat_in` and `dat_in_sum_day` called?  

:::

::::


# Example 3

```{r}
#| output-location: column
library(gapminder)

gapminder_yr_2007 <- gapminder %>% 
  filter(year == 2007)

ggplot(data = gapminder_yr_2007, 
       mapping = aes(x = continent, 
                     y = lifeExp)) +
  geom_boxplot(outlier.shape = NA) + # google this
  geom_jitter(position = position_jitter(width = 0.1, height = 0),
              alpha = 1/4, size = 3) +
  labs(x = NULL,
       y = "life expectancy") +
  theme_minimal(base_size = 14) 


```


# Data Science Lifecycle {background-color="#0F4C81"}

# 1 {background-image="img/data-science-lifecycle/data-science-lifecycle.001.png"}

# 2 {background-image="img/data-science-lifecycle/data-science-lifecycle.002.png"}

# 3 {background-image="img/data-science-lifecycle/data-science-lifecycle.003.png"}

# 4 {background-image="img/data-science-lifecycle/data-science-lifecycle.004.png"}

# 5 {background-image="img/data-science-lifecycle/data-science-lifecycle.005.png"}

# 6 {background-image="img/data-science-lifecycle/data-science-lifecycle.006.png"}

# 7 {background-image="img/data-science-lifecycle/data-science-lifecycle.007.png"}

# Homework {background-color="#0F4C81"}

## {background-iframe="https://rbtl-fs22.github.io/website/am-05-data-management.html"}

# Thanks! 

## Thanks! `r emo::ji("sunflower")` 

Slides created via Quarto: https://quarto.org/docs/presentations/revealjs/ 

Access slides as [PDF on GitHub](https://rbtl-fs22.github.io/website/slides/pt2-d02-tools/pt2-d02-tools.pdf)

All material is licensed under [Creative Commons Attribution Share Alike 4.0 International](https://creativecommons.org/licenses/by-sa/4.0/). 

# Templates

## Background iFrame {background-iframe="https://rbtl-fs22.github.io/website/am-05-data-management.html"}

## Tabsets

::: {.panel-tabset}

### Tab A

Content for `Tab A`

### Tab B

Content for `Tab B`

:::

## Columns

:::: {.columns}

::: {.column width="40%"}

### Left column

```{r}
library(dplyr)
```

:::

::: {.column width="60%"}
### Right column

```{r}
print(mtcars)
```

:::

::::

## Code Animations

## {auto-animate="true"}

```r
# Fill in the spot we created for a plot
output$phonePlot <- renderPlot({
  # Render a barplot
})
```

## {auto-animate=true}

```r
# Fill in the spot we created for a plot
output$phonePlot <- renderPlot({
  # Render a barplot
  barplot(WorldPhones[,input$region]*1000, 
          main=input$region,
          ylab="Number of Telephones",
          xlab="Year")
})
```

# Preview Links

## Preview Links
 
[Preview](https://rbtl-fs22.github.io/website/){preview-link="true"}
