---
title: "rbtl - Research Beyond the Lab"
subtitle: "Data Science Lifecycle"  
author: "Lars Schöbitz"
institute: "Global Health Engineering - ETH Zurich"
date: '
  `r Sys.Date()`'
format: 
  revealjs: 
    theme: [default, "../slides.scss"]
    chalkboard: true
editor: source
---

```{r}
#| child: "../setup.Rmd"
```

```{r}
library(tidyverse)
library(lubridate)
library(gapminder)
```

```{r data}

dat_link <- "https://raw.githubusercontent.com/Global-Health-Engineering/manuscript-hospital-air-quality/main/data/intermediate/malawi-hospitals-air-quality.csv"

# The following codee uses a function calles 'read_csv()' to read the data from 
# the link that is stored in the Object dat_link. The data is then stored in a 
# new object named 'dat_in'. After running the code, the name shows up in the   
# Environment pane in the top right of window 

dat_in <- read_csv(dat_link)

dat_in_sum_day <- dat_in %>% 
  filter(value <= 1000) %>% 
  mutate(date = lubridate::as_date(date_time)) %>% 
  group_by(date, location, indicator) %>% 
  summarise(min = min(value),
            median = median(value),
            mean = mean(value),
            sd = sd(value),
            max = max(value)) %>% 
  ungroup()

```

# Welcome back!

## What's next?

- Classroom tools
- Data Science Lifecycle
- R: Functions, Arguments, Objects, Operators
- Live Coding Exercise
- Pair Programming Exercise
- GitHub Teams
- Assignment Week 10: Data submission

# Classroom tools

## Live Coding Exercises

- Instructor writes and narrates code out loud 
- Intstructor explains elements and principles that are relevant
- Code is displayed on projector screen
- Learners join by writing and executing the same code
- Learners "code-along" with the instructor

## Pair Programming Exercises

- Two learners work together on one computer
- One person (the driver) does the typing
- The other person (the navigator) offers comments and suggestions
- Roles get switched

## Taking Notes Together

- Questions in shared online document: [TODO]

## Sticky Notes 

- Use as status flags
- Green: Exercise completed
- Orange: Problem, need support.

# Data Science Lifecycle {background-color="#0F4C81"}

# 1 {background-image="img/data-science-lifecycle/data-science-lifecycle.001.png"}

# 2 {background-image="img/data-science-lifecycle/data-science-lifecycle.002.png"}

# 3 {background-image="img/data-science-lifecycle/data-science-lifecycle.003.png"}

# 4 {background-image="img/data-science-lifecycle/data-science-lifecycle.004.png"}

# 5 {background-image="img/data-science-lifecycle/data-science-lifecycle.005.png"}

# 6 {background-image="img/data-science-lifecycle/data-science-lifecycle.006.png"}

# 7 {background-image="img/data-science-lifecycle/data-science-lifecycle.007.png"}

# R

## Packages {auto-animate="true"}

::: {.incremental}

:::: {.columns}

::: {.column width="40%"}

**base R**

```{r}
#| eval: false
#| echo: true
sqrt(49)
sum(1, 2)
```

- Functions come with R

:::

::: {.column width="5%"}

:::

::: {.column width="55%"}

**R Packages**

```{r}
#| eval: false
#| echo: true
library(dplyr)

```

- Installed once in the Console: `install.packages("dplyr")`
- Loaded per script

:::

::::

:::

## Functions & Arguments {auto-animate="true"}

```{r}
#| code-line-numbers: "3-4"
#| eval: false
#| echo: true
library(dplyr)

filter(.data = gapminder, 
       year == 2007)
```

- Function: `filter()`
- Argument: `.data = ` 
- Arguments following: `year == 2007` **What do do with the data**

## Objects {auto-animate="true"}

```{r}
#| eval: false
#| code-line-numbers: "3-4"
#| echo: true
library(dplyr)

gapminder_yr_2007 <- filter(.data = gapminder, 
       year == 2007)
```

- Function: `filter()`
- Argument: `.data = `
- Arguments following: `year == 2007` **What do do with the data**
- Object: `gapminder_yr_2007`

## Operators {auto-animate="true"}

```{r}
#| eval: false
#| code-line-numbers: "3-4"
#| echo: true
library(dplyr)

gapminder_yr_2007 <- gapminder %>% 
  filter(year == 2007) 
```

- Function: `filter()`
- Argument: `.data = `
- Arguments following: `year == 2007` **What do do with the data**
- Object: `gapminder_yr_2007`
- Assignment operator: `<-`
- Pipe operator: `%<%`

## Rules

Rules of `dplyr` functions:

::: {.incremental}

- First argument is always a data frame
- Subsequent arguments say what to do with that data frame
- Always return a data frame  
- Don't modify in place 

:::

# Live Coding Exercise 

## ae-10-data-science-lifecycle

1. Head over to the GitHub Organisation for the course.
2. Find the repo for week 10 that has your GitHub username.
3. Clone the repo with your username to the RStudio Cloud.
4. Open the file: `ae-10a-lifecycle.qmd`
4. Use your Sticky Notes to let me know when you are ready.

# Pair Programming

## ae-10-data-science-lifecycle

1. Team up in pairs.
2. Decide who writes code, and who supports without writing code.
3. Open the file: `ae-10b-lifecycle.qmd`
3. Work through the exercises.

```{r}

countdown(
  minutes = 15, seconds = 0,
  left = 0, right = 0,
  padding = "10px", margin = "5%",
  font_size = "2em"
)

```

# Homework {background-color="#0F4C81"}

## Research Project Template

- One repository for each team (group)
- Template for research project report
- Complete list of items for grading (also here: [TODO])

## Report writing process

- Decide who uploads the raw data
- Everyone writes 'Results & Discussion' from this week
- Other chapters are worked on collaboratively from next week
- You organise yourself to get the report done

## Workflow

- First: Pull, Pull, Pull
- Then: Render, Add, Commit, Push

## Assignment

- Report is not the homework assignment
- Separate homework assignments (2 points) to practise concepts from class
- Hand in by Tuesday, 23:59 the following week 


## {background-iframe="https://rbtl-fs22.github.io/website/am-05-data-management.html"}


# Weekly Evaluation



# Thanks! 

## Thanks! `r emo::ji("sunflower")` 

Slides created via Quarto: https://quarto.org/docs/presentations/revealjs/ 

Access slides as [PDF on GitHub](https://rbtl-fs22.github.io/website/slides/pt2-d02-tools/pt2-d02-tools.pdf)

All material is licensed under [Creative Commons Attribution Share Alike 4.0 International](https://creativecommons.org/licenses/by-sa/4.0/). 

# Templates

## Background iFrame {background-iframe="https://rbtl-fs22.github.io/website/am-05-data-management.html"}

## Tabsets

::: {.panel-tabset}

### Tab A

Content for `Tab A`

### Tab B

Content for `Tab B`

:::

## Columns

:::: {.columns}

::: {.column width="40%"}

### Left column

```{r}
library(dplyr)
```

:::

::: {.column width="60%"}
### Right column

```{r}
print(mtcars)
```

:::

::::

## Code Animations

## {auto-animate="true"}

```r
# Fill in the spot we created for a plot
output$phonePlot <- renderPlot({
# Render a barplot
})
```

## {auto-animate=true}

```r
# Fill in the spot we created for a plot
output$phonePlot <- renderPlot({
# Render a barplot
barplot(WorldPhones[,input$region]*1000, 
main=input$region,
ylab="Number of Telephones",
xlab="Year")
})
```

# Preview Links

## Preview Links

[Preview](https://rbtl-fs22.github.io/website/){preview-link="true"}
